Scottish Child Payment Interventions

### 2024-01-24 minos/outcomes/SCP_vis_summary.Rmd
Small addition to datain summary scripts for better memory handling, and set new path for SCP_vis_summary

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')
#out.path <- here::here('output', 'default_config_batch')
out.path <- here::here('output', 'scaled_scotland_batch', 'summary_files')

>>>>

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')
#out.path <- here::here('output', 'default_config_batch')
out.path <- here::here('output', 'scaled_scotland_10', 'summary_files')
